Numerical simulation of the Cordilleran ice sheet through the last glacial cycle

### 2014-06-11 cordillera-cycle.tex
Update notes and todos.

\todo{Small adjustments to avoid repetitions with the previous paper.}

@@

\todo{Develop the three subsections in order to reach the conclusions.}

@@

% fig:timeseries
\begin{figure}
  \includegraphics{timeseries}
  \caption{Temperature offset time-series from ice core and sediment core
           records (Table~\ref{tab:records}) used as palaeo-climate forcing for
           the ice sheet model \textbf{(top)}, and modelled ice volume
           through the last 120\,\unit{kyr}, expressed in meters of sea-level
           equivalent \textbf{(bottom)}. Gray spans indicate Marine Isotope
           Stages (MIS) according to a global compilation of benthic
           \chem{\delta^{18}O} records \citep{lisiecki-raymo-2005}. Hatched
           rectangles highlight modelled ice volume extrema corresponding to
           MIS~4 (61.9--55.4\,\unit{kyr}), MIS~3 (52.2--45.6\,\unit{kyr}), and
           MIS~2 (last glacial maximum, 29.5--16.9\,\unit{kyr}). Dotted lines
           correspond to the GRIP and EPICA 6\,\unit{km}-resolution runs.}
  \label{fig:timeseries}
\end{figure}

@@

% fig:erosion
\begin{figure}
  \includegraphics{erosion}
  \caption{Modelled cumulative basal displacement (integrand of basal velocity)
           over the last 120\,\unit{kyr}.
           \note{Even after carefully adjusting the colours, I still find this
                 figure quite ugly and feel that it does not show much. I may
                 remove it from this paper and keep the idea for later use.}}
  \label{fig:erosion}
\end{figure}

% fig:deglacseries
\begin{figure}
  \includegraphics{deglacseries}
  \caption{Temperature offset time-series from the GRIP and EPICA ice core
           records (Table~\ref{tab:records}) \textbf{(top)}, and modelled ice
           volume during the deglaciation, expressed in meters of sea-level
           equivalent \textbf{(bottom)}.}
  \label{fig:deglacseries}
\end{figure}

@@

% fig:deglacshots
\begin{figure}
  \includegraphics{deglacshots}
  \caption{Snapshots of modelled surface topography (200\,\unit{m} contours)
           and surface velocity (colour mapping) from the GRIP simulation,
           corresponding to the last glacial maximum (-19.5 kyr) and the last
           deglaciation.}
  \label{fig:deglacshots}
\end{figure}

% fig:profiles
\begin{figure}
  \includegraphics{profiles}
  \caption{Modelled bedrock (black) and ice surface (blue) topography profiles
           during deglaciation (22.0--8.0\,\unit{kyr}) in the GRIP 6\,\unit{km}
           simulation, corresponding to the four transects indicated in
           Fig.~\ref{fig:deglac}.}
  \label{fig:profiles}
\end{figure}

>>>>

@@

@@

% fig:timeseries
\begin{figure}
  \includegraphics{timeseries}
  \caption{Temperature offset time-series from ice core and sediment core
           records (Table~\ref{tab:records}) used as palaeo-climate forcing for
           the ice sheet model \textbf{(top)}, and modelled ice volume
           through the last 120\,\unit{kyr}, expressed in meters of sea-level
           equivalent \textbf{(bottom)}. Gray spans indicate Marine Isotope
           Stages (MIS) according to a global compilation of benthic
           \chem{\delta^{18}O} records \citep{lisiecki-raymo-2005}. Hatched
           rectangles highlight modelled ice volume extrema corresponding to
           MIS~4 (61.9--55.4\,\unit{kyr}), MIS~3 (52.2--45.6\,\unit{kyr}), and
           MIS~2 (last glacial maximum, 29.5--16.9\,\unit{kyr}). Dotted lines
           correspond to the GRIP and EPICA 6\,\unit{km}-resolution runs.
           \todo{add grid lines to improve readability}}
  \label{fig:timeseries}
\end{figure}

@@

% fig:erosion
\begin{figure}
  \includegraphics{erosion}
  \caption{Modelled cumulative basal displacement (integrand of basal velocity)
           over the last 120\,\unit{kyr}.
           \note{I am still unsure about the use of this figure. I may
                 remove it from this paper and keep the idea for later use.}}
  \label{fig:erosion}
\end{figure}

% fig:deglacseries
\begin{figure}
  \includegraphics{deglacseries}
  \caption{Temperature offset time-series from the GRIP and EPICA ice core
           records (Table~\ref{tab:records}) \textbf{(top)}, and modelled ice
           volume during the deglaciation, expressed in meters of sea-level
           equivalent \textbf{(bottom)}.
           \todo{add grid lines to improve readability}}
  \label{fig:deglacseries}
\end{figure}

@@

% fig:deglacshots
\begin{figure}
  \includegraphics{deglacshots}
  \caption{Snapshots of modelled surface topography (200\,\unit{m} contours)
           and surface velocity (colour mapping) from the GRIP simulation,
           corresponding to the last glacial maximum (-19.5 kyr) and the last
           deglaciation.
           \note{should we have a similar figure using EPICA?}}
  \label{fig:deglacshots}
\end{figure}

% fig:profiles
\begin{figure}
  \includegraphics{profiles}
  \caption{Modelled bedrock (black) and ice surface (blue) topography profiles
           during deglaciation (22.0--8.0\,\unit{kyr}) in the GRIP 6\,\unit{km}
           simulation, corresponding to the four transects indicated in
           Fig.~\ref{fig:deglac}.
           \note{should we have a similar figure using EPICA?}}
  \label{fig:profiles}
\end{figure}
